Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information

### 2019-05-23 manuscript/supporting_info.tex
checked bib, ready to send out revamped discussion

\author{Alyssa R. Cirtwill$^{1}$, Giulio V. Dalla Riva$^{2}$, Nick J. Baker$^{1}$,\\
 Joshua A. Thia$^{1,3}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$, MSC helpers from Linkoping}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
    \medskip$^2$Biomathematics Research Centre, School of Mathematics and Statistics\\
            University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^3$Present Address: School of Biological Sciences\\
University of Queensland\\Brisbane, QLD 4072, Australia }

@@

\section*{Supporting information 1: Sources for networks}
  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses.}
    \label{sources}
    \begin{center}
    \begin{tabular}{|l l m{6cm} |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_001  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_002  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_003  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_004  & Pollination & \citep{Barrett1987} \\
    M\_PL\_005  & Pollination & \citep{Clements1923}  \\
    M\_PL\_006  & Pollination & \citep{Dicks2002} \\
    M\_PL\_007  & Pollination & \citep{Dicks2002} \\
    M\_PL\_008  & Pollination & \citep{Dupont2003}  \\
    M\_PL\_009  & Pollination & \citep{Elberling1999} \\
    M\_PL\_010  & Pollination & Elberling, H. \& Olesen, J. M. Unpublished. \\
    M\_PL\_011  & Pollination & \citep{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_013  & Pollination & \citep{Ollerton2003}  \\
    M\_PL\_014  & Pollination & \citep{Hocking1968} \\
    M\_PL\_015  & Pollination & \citep{Petanidou1991} \\
    M\_PL\_016  & Pollination & \citep{Herrera1988} \\
    M\_PL\_017  & Pollination & \citep{Memmott1999} \\
    M\_PL\_018  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & \citep{Inouye1988}  \\
    M\_PL\_020  & Pollination & \citep{Kevan1970} \\
    M\_PL\_021  & Pollination & \citep{Kato1999}  \\
    M\_PL\_022  & Pollination & \citep{Medan2002} \\
    M\_PL\_023  & Pollination & \citep{Medan2002} \\
    M\_PL\_024  & Pollination & \citep{Mosquin1967} \\
    M\_PL\_025  & Pollination & \citep{Motten1982}  \\
    M\_PL\_026  & Pollination & \citep{McMullen1993}  \\
    M\_PL\_027  & Pollination & \citep{Primack1983} \\
    M\_PL\_028  & Pollination & \citep{Primack1983} \\
    M\_PL\_029  & Pollination & \citep{Primack1983} \\
    M\_PL\_030  & Pollination & \citep{Ramirez1992} \\
    M\_PL\_031  & Pollination & \citep{Ramirez1989} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table}

@@

    \begin{table*}[h!]
    \begin{center}
    \begin{tabular}{|l l m{6cm} |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_032  & Pollination & \citep{Schemske1978}  \\
    M\_PL\_033  & Pollination & \citep{Small1976} \\
    M\_PL\_034  & Pollination & \citep{SmithRamirez2005}  \\
    M\_PL\_035  & Pollination & \citep{Percival1974}  \\
    M\_PL\_036  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_037  & Pollination & \citep{Montero2005} \\
    M\_PL\_038  & Pollination & \citep{Montero2005} \\
    M\_PL\_039  & Pollination & \citep{Stald2003} \\
    M\_PL\_040  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_041  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_042  & Pollination & \citep{Philipp2006} \\
    M\_PL\_043  & Pollination & \citep{Montero2005} \\
    M\_PL\_044  & Pollination & \citep{Kato2000}  \\
    M\_PL\_045  & Pollination & \citep{Lundgren2005}  \\
    M\_PL\_046  & Pollination & \citep{Bundgaard2003} \\
    M\_PL\_047  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_048  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_049  & Pollination & \citep{Beks2006}  \\
    M\_PL\_050  & Pollination & \citep{Stald2003} \\
    M\_PL\_051  & Pollination & \citep{Vazquez2002} \\
    M\_PL\_052  & Pollination & \citep{Witt1998}  \\
    M\_PL\_053  & Pollination & \citep{Yamazaki2003}  \\
    M\_PL\_054  & Pollination & \citep{Kakutani1990}  \\
    M\_PL\_055  & Pollination & \citep{Kato1996}  \\
    M\_PL\_056  & Pollination & \citep{Kato1993}  \\
    M\_PL\_057  & Pollination & \citep{Inoue1990} \\
    M\_PL\_058  & Pollination & \citep{Bartomeus2008} \\
    M\_PL\_059  & Pollination & \citep{Bezerra2009} \\
    Basset  & Herbivory & \citep{Basset1999}  \\
    Bluthgen  & Herbivory & \citep{Bluthgen2006}  \\
    Bodner  & Herbivory & \citep{Bodner2010}  \\
    Coley & Herbivory & \citep{Coley2006} \\
    Ibanez  & Herbivory & \citep{Ibanez2013}  \\
    Joern\_altuda  & Herbivory & \citep{Joern1979} \\
    Joern\_marathon  & Herbivory & \citep{Joern1979} \\
    Novotny & Herbivory & \citep{Novotny2012} \\
    Peralta & Herbivory & \citep{Peralta2015} \\
    Sheldon & Herbivory & \citep{Sheldon1978} \\
    Ueckert & Herbivory & \citep{Ueckert1971} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table*}
\clearpage
\newpage

@@

@@

\newpage
\bibliographystyle{newphy}
\renewcommand*{\bibfont}{\raggedright}
\bibliography{noisn}

>>>>

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
\medskip$^2$Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
University of Queensland\\Brisbane, QLD 4072, Australia }

@@

\section*{Supporting information 1: Sources for networks}
  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses.}
    \label{sources}
    \begin{center}
    \begin{tabular}{|l l m{10cm} |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_001  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_002  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_003  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_004  & Pollination & \citep{Barrett1987} \\
    M\_PL\_005  & Pollination & \citep{Clements1923}  \\
    M\_PL\_006  & Pollination & \citep{Dicks2002} \\
    M\_PL\_007  & Pollination & \citep{Dicks2002} \\
    M\_PL\_008  & Pollination & \citep{Dupont2003}  \\
    M\_PL\_009  & Pollination & \citep{Elberling1999} \\
    M\_PL\_010  & Pollination & Elberling, H. \& Olesen, J. M. Unpublished. \\
    M\_PL\_011  & Pollination & \citep{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_013  & Pollination & \citep{Ollerton2003}  \\
    M\_PL\_014  & Pollination & \citep{Hocking1968} \\
    M\_PL\_015  & Pollination & \citep{Petanidou1991} \\
    M\_PL\_016  & Pollination & \citep{Herrera1988} \\
    M\_PL\_017  & Pollination & \citep{Memmott2002} \\
    M\_PL\_018  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & \citep{Inouye1988}  \\
    M\_PL\_020  & Pollination & \citep{Kevan1970} \\
    M\_PL\_021  & Pollination & \citep{Kato1990}  \\
    M\_PL\_022  & Pollination & \citep{Medan2002} \\
    M\_PL\_023  & Pollination & \citep{Medan2002} \\
    M\_PL\_024  & Pollination & \citep{Mosquin1967} \\
    M\_PL\_025  & Pollination & \citep{Motten1982}  \\
    M\_PL\_026  & Pollination & \citep{McMullen1993}  \\
    M\_PL\_027  & Pollination & \citep{Primack1983} \\
    M\_PL\_028  & Pollination & \citep{Primack1983} \\
    M\_PL\_029  & Pollination & \citep{Primack1983} \\
    M\_PL\_030  & Pollination & \citep{Ramirez1992} \\
    M\_PL\_031  & Pollination & \citep{Ramirez1989} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table}

@@

    \begin{table*}[h!]
    \begin{center}
    \begin{tabular}{|l l m{6cm} |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_032  & Pollination & \citep{Schemske1978}  \\
    M\_PL\_033  & Pollination & \citep{Small1976} \\
    M\_PL\_034  & Pollination & \citep{SmithRamirez2005}  \\
    M\_PL\_035  & Pollination & \citep{Percival1974}  \\
    M\_PL\_036  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_037  & Pollination & \citep{Montero2005} \\
    M\_PL\_038  & Pollination & \citep{Montero2005} \\
    M\_PL\_039  & Pollination & \citep{Stald2003} \\
    M\_PL\_040  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_041  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_042  & Pollination & \citep{Philipp2006} \\
    M\_PL\_043  & Pollination & \citep{Montero2005} \\
    M\_PL\_044  & Pollination & \citep{Kato2000}  \\
    M\_PL\_045  & Pollination & \citep{Lundgren2005}  \\
    M\_PL\_046  & Pollination & \citep{Bundgaard2003} \\
    M\_PL\_047  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_048  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_049  & Pollination & \citep{Bek2006}  \\
    M\_PL\_050  & Pollination & \citep{Stald2003} \\
    M\_PL\_051  & Pollination & \citep{Vazquez2002} \\
    M\_PL\_052  & Pollination & \citep{Witt1998}  \\
    M\_PL\_053  & Pollination & \citep{Yamazaki2003}  \\
    M\_PL\_054  & Pollination & \citep{Kakutani1990}  \\
    M\_PL\_055  & Pollination & \citep{Kato1996}  \\
    M\_PL\_056  & Pollination & \citep{Kato1993}  \\
    M\_PL\_057  & Pollination & \citep{Inoue1990} \\
    M\_PL\_058  & Pollination & \citep{Bartomeus2008} \\
    M\_PL\_059  & Pollination & \citep{Bezerra2009} \\
    Basset  & Herbivory & \citep{Basset1996}  \\
    Bluthgen  & Herbivory & \citep{Bluthgen2006}  \\
    Bodner  & Herbivory & \citep{Bodner2010}  \\
    Coley & Herbivory & \citep{Coley2006} \\
    Ibanez  & Herbivory & \citep{Ibanez2013}  \\
    Joern\_altuda  & Herbivory & \citep{Joern1979} \\
    Joern\_marathon  & Herbivory & \citep{Joern1979} \\
    Novotny & Herbivory & \citep{Novotny2012} \\
    Peralta & Herbivory & \citep{Peralta2016} \\
    Sheldon & Herbivory & \citep{Sheldon1978} \\
    Ueckert & Herbivory & \citep{Ueckert1971} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table*}
\clearpage
\newpage

@@

    Comparing the permuted networks to permutations of the permuted networks, the slope obtained from the initial permuted network showed no clear relationship to the slopes obtained from 500 permutations of the permuted network. Averaged over the 1000 permutations of each observed network, the slope of the permuted network was more extreme than 48.1-51.3\% of the permutations of the permuted network. This confirms that shuffling phylogenetic distances between plant pairs destroys the relationship between distance and interaction partner overlap, and that further shuffling distances does not have a predictable effect.

@@

\newpage
\bibliographystyle{newphy}
\renewcommand*{\bibfont}{\raggedright}
\bibliography{manual}
